On exponential sums arising from the classical doubling method

### 2025-04-01 main.tex
Defining notation

\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblPosVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblNegVirtualJacobiSumScalar}[2]{\mathrm{j}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}
\newcommand{\SymmetricGroup}{\mathfrak{S}}

@@

Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
$$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$

\elad{Need to define $2 \lambda$ and $\FieldNorm{2\lambda}{\lambda}$ and $\NormOneGroup{2 \lambda}$}

>>>>

\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblPosVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblNegVirtualJacobiSumScalar}[2]{\mathrm{j}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}
\newcommand{\SymmetricGroup}{\mathfrak{S}}
\newcommand{\Kernel}{\operatorname{Ker}}

@@

Given an integer $m \ge 1$ we define $$\NormOneGroup{2m} = \Kernel \FieldNorm{2m}{m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right) = 1\right\}.$$

Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
$$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$
We also define $2 \lambda = \left(2 \lambda_1, \dots, 2 \lambda_{\ell}\right)$ and $\aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}} \colon \multiplicativegroup{\finiteFieldExtension{2 \lambda}} \to \multiplicativegroup{\finiteFieldExtension{\lambda}}$ by $$\aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}}\left(x_1,\dots,x_{\ell}\right) = \left(\FieldNorm{2\lambda_1}{\lambda_1}\left(x_1\right), \dots, \FieldNorm{2\lambda_{\ell}}{\lambda_{\ell}}\left(x_{\ell}\right)\right).$$
This is the restriction to $\multiplicativegroup{\finiteFieldExtension{2 \lambda}}$ of the norm map given by viewing $\finiteFieldExtension{2\lambda}$ as an algebra over $\finiteFieldExtension{\lambda}$. We define $$\NormOneGroup{2\lambda} = \Kernel \aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}} = \left\{x \in \multiplicativegroup{\finiteFieldExtension{2\lambda}} \mid \aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}}\left(x\right) = 1\right\},$$
where $\multiplicativegroup{\finiteField} \to \multiplicativegroup{\finiteFieldExtension{\lambda}}$ is embedded diagonally. It is clear that $$\NormOneGroup{2\lambda} = \prod_{i=1}^{\ell} \NormOneGroup{2 \lambda_j}.$$
